Allowing Stable Groups of Prosumers to Enter the Market through Proper Aggregation

### 2014-09-12 Article.tex
update the introduction

In section \ref{sec:model}, we considered agents production that depend on meteorological conditions (wind turbines and PV as generators), various energy mix and preferences, their appliances (loads and generators). We used real meteorological data (see section \ref{subsec:ProsumerModel}) to account for seasonal and daily variations in the prosumer's energetic profiles as well as realistic geographical correlations between different agents. With these ingredients, we are able to run realistic simulations and record the different output profiles as time-series.

As correlations play a significant role in our mechanism, we organize the prosumers in a correlation graph, a quite popular approach in market stocks clustering since \cite{Mantegna1999}. We will see that in such graphs, cliques represent structures of interest. In our settings, it means that cliques are “good” (from the utility point of view) foundations for high valued coalitions. We thereby use a modified clique percolation algorithm (see section \ref{sec:results}) that will enable us to expand the cliques as much as needed in order to form proper coalitions that fulfill grid requirements. Finally, in section \ref{sec:results} provides some results and a conclusion in section \ref{sec:conclusion}.

>>>>

In section \ref{sec:model}, we considered agents production that depend on meteorological conditions (wind turbines and PV as generators), various energy mix and preferences, their appliances (loads). We used meteorological data (see section \ref{subsec:ProsumerModel}) to account for seasonal and daily variations in the prosumer's energetic profiles as well as realistic geographical correlations between different agents. With these ingredients, we are able to run realistic simulations and record the different output profiles as time-series.

In order to select group prosumer that lower the volatility of the coalition's production, we define an algorithm based on a popular approach for stocks market clustering \cite{Mantegna1999}. In our settings, we claim that cliques are "good" from the utility point of view and thereby we use a modified clique percolation algorithm (see section \ref{sec:forming}) that will enable us to expand the cliques as much as needed in order to form proper coalitions that fulfill both the grid requirements and lower the production volatility. Finally, in section \ref{sec:results} provides some results and a conclusion in section \ref{sec:conclusion}.
